Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-03 main.Rmd
p27 the package gs is not easy to find. Should almanac and gs both be referenced?
grammar

(ref:allFig) Distribution of energy consumption displayed through letter value plots: (a) across month-of-year faceted by quarter-of-year; (b) across weekday/weekend faceted by quarter-of-year; (c) across quarter-of-year faceted by weekday/weekend. Plot (a) shows a clash since there are empty combinations. Plots (b) and (c) show harmonies since each quarter includes both weekdays and weekends. It can be seen in (b) that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently. Plot (c) switch the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends.

@@

A missing piece in the package `gravitas` is the computation of cyclic aperiodic granularities which would require computing aperiodic linear granularities first. A few R packages including `almanac`[@R-almanac] and `gs` provide the tools to create recurring aperiodic events. These functions can be used with the `gravitas` package to accommodate aperiodic cyclic granularities.

>>>>

(ref:allFig) Distribution of energy consumption displayed through letter value plots: (a) across month-of-year faceted by quarter-of-year; (b) across weekday/weekend faceted by quarter-of-year; (c) across quarter-of-year faceted by weekday/weekend. Plot (a) shows a clash since there are empty combinations. Plots (b) and (c) show harmonies since each quarter includes both weekdays and weekends. It can be seen in (b) that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently. Plot (c) switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends.

@@

A missing piece in the package `gravitas` is the computation of cyclic aperiodic granularities which would require computing aperiodic linear granularities first. A few R packages including `almanac`[@R-almanac] and `gs`[@R-gs] provide the tools to create recurring aperiodic events. These functions can be used with the `gravitas` package to accommodate aperiodic cyclic granularities.
